PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-21 paper.tex
More restructuring

\section{Research Questions and Hypotheses}

\subsection{Game Dynamics}

\subsection{Social Dynamics}

\subsection{Mental representations}

\subsection{Interplay between these questions}

@@

\resizebox{\linewidth}{!}{%
\begin{tikzpicture}[
                font=\sffamily,
                >=latex,
                every edge/.style={draw, very thick},
                node/.style={draw, rounded corners, align=center, inner sep=5pt, fill=black!20},
                label/.style={midway, align=center, font=\scriptsize\sffamily, fill=white}]

@@

@@

During the acquisition campaign for the PinSoRo dataset, we have also recorded a
\emph{child-robot} interaction baseline. We were using the exact same protocol
as described above, only with one child replaced by a Nao robot.

The robot was fully autonomous, and programmed to exhibit a non-social behaviour
(its action policy was simply to repeatedly move interactive items to
pre-defined zones, entierly ignoring its child partner).

>>>>

\subsection{Specific research questions}

@@

\resizebox{0.8\linewidth}{!}{%
\begin{tikzpicture}[
                font=\sffamily,
                >=latex,
                every edge/.style={draw, very thick},
                node/.style={draw, rounded corners, align=center, inner sep=5pt, fill=black!20},
                label/.style={midway, align=center, font=\scriptsize\sffamily, fill=white}]

@@

\subsubsection{Game Dynamics}

\subsubsection{Social Dynamics}

\subsubsection{Mental representations}

@@

During the acquisition campaign for the PInSoRo dataset, we have also recorded a
\emph{child-robot} interaction baseline. We were using the exact same protocol
as described above, only with one child replaced by a Nao robot.

The robot was fully autonomous, and programmed to exhibit a non-social behaviour
(its action policy was simply to repeatedly move interactive items to
pre-defined zones, entirely ignoring its child partner).
